---
title: "Summary of Exploratory Tasks"
author: 'Valerie De La Fuente, Mai Uyen Thanh Huynh, Casey Alexander Linden, Nazhah Mir'
date: 11/20/24
---

### HTML scraping

Does including header content improve predictions? Answer the question and provide quantitative evidence supporting your answer.

```{r}
load("../data/claims_clean_headers_metrics.RData")
claims_clean_headers_metrics
```

```{r}
load("../data/claims_clean_no_headers_metrics.RData")
claims_clean_no_headers_metrics
```


### Bigrams

Do bigrams capture additional information relevant to the classification of interest? Answer the question, **briefly** describe what analysis you conducted to arrive at your answer, and provide quantitative evidence supporting your answer.

```{r}
load("../data/claims_clean_bigrams_metrics.RData")
claims_clean_bigrams_metrics
```

### Neural net

Summarize the neural network model you trained by desribing:

-   architecture

-   optimization and loss

-   training epochs

-   predictive accuracy
