---
title: "Summary of Exploratory Tasks"
author: 'Valerie De La Fuente, Mai Uyen Thanh Huynh, Casey Alexander Linden, Nazhah Mir'
date: 11/20/24
---
## Introduction
This report summarizes the methodology and results of incorporating header information and bigram tokenization in webpage classification based on scraping text content.

## HTML scraping

### Methodology

The data with headers, `claims-clean-headers`, is transformed into a TF-IDF to identify words that are significant to a particular webpage. Principal component analysis is performed on the training data matrix to project it onto a lower-dimensional subspace. 211 principal components were used in the projection. Then, a logistic regression model is trained to predict the binary class based on the principal component analysis projections. The test data matrix is projected into the same lower-dimensional subspace, and predictions for the test set are generated using the logistic regression model. 

Class metrics are calculated on the test predictions, and the output is as follows:
```{r}
load("../data/claims_clean_headers_metrics.RData")
claims_clean_headers_metrics
```

The same process is applied to the data without headers, `claims-clean`, and the output from the class metrics is as follows:
```{r}
load("../data/claims_clean_no_headers_metrics.RData")
claims_clean_no_headers_metrics
```

### Results
The data with headers has sensitivity of 0.8044 and specificity of 0.7436, while the data without headers has a sensitivity of 0.8468 and specificity of 0.7861. This indicates that the data with headers correctly identifies true positives and true negatives at a lower rate than the data without headers. The accuracy of the predictions of the data with headers is at 0.7761 and the accuracy of the data without headers is at 0.8202, suggesting that including header content did not improve predictions. Surprisingly, the data with headers has a ROC AUC of 0.8705, around 0.01 higher than that of the data without headers. This contrast illustrates that the data with headers may have higher discriminatory ability, while the data without headers has better classification performance in terms of final predictions.

## Bigrams

Do bigrams capture additional information relevant to the classification of interest? Answer the question, **briefly** describe what analysis you conducted to arrive at your answer, and provide quantitative evidence supporting your answer.

```{r}
load("../data/claims_clean_bigrams_metrics.RData")
claims_clean_bigrams_metrics
```

